Landau quantization of nearly degenerate bands

### 2018-09-23 paper.tex
Updates from ShareLaTeX

\begin{figure}
\includegraphics[width=1.0\columnwidth]{RD.png}
% alpha=0.05
% beta=0.02
% m=0.01
\caption{Rashba-Dresselhaus model. (a) Typical cyclotron orbits. (b) Comparison of Landau levels calculated by Eq. (\ref{eq:rule}) (black lines) and numerical diagonalization of the Peierls-Onsager Hamiltonian  $H_{RD}(\bK)$ (red dots). Parameters for (b): $\alpha=0.05$(eV$\cdot$\AA), $m=0.01$($\hbar^2$/eV$\cdot$\AA$^2$), $\beta=0.02~(0.04)$(eV$\cdot$\AA) for left (right) panels. (c) For various spin-orbit parameters $(\alpha,\beta)$ of the Rashba-Dresselhaus model and various field strength (satisfying $l^2S(E)\gg 1$), we plot  $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that lies closest to energy $E=0.4eV$, where $\epsilon_\text{rule}$ is determined by Eq. (\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian  $H_{RD}(\bK)$. We also plot in (d) $l^2\delta S^2/S$, which has a strong positive relation with error in (c). Parameters for (c-d): $m=0.01$($\hbar^2$/eV$\cdot$\AA$^2$). Units: $\alpha$($10^{-2}$eV$\cdot$\AA), $\beta$($10^{-2}$eV$\cdot$\AA), $Z$($10^{-3}$eV), $l^2 S$($10^2$).\label{fig:RD}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1.0\columnwidth]{RZ.png}
\caption{(a) Trefoille-shaped cyclotron orbit for the Rashba-Zeeman model at the energy of the Dirac point. The orbit is drawn over the  spin-splitting field ($d_x,d_y$) of the Hamiltonian $H_{RZ}{=}d_0(\bk)I{+}d_x(\bk)\sigma_x{+}d_y(\bk)\sigma_y$, with $d_j$ obtainable from \q{eq:RZ-Hamiltonian}. The wavefunction along the inner (resp.\ outer) component of the trefoille orbit has its pseudospin aligned parallel (resp.\ anti-parallel) to the spin-orbit field. (b) Black dashed lines illustrate a zeroth-order approximation of the Landau levels (assuming Klein tunneling); the leading-order correction is indicated by red lines. Exact Landau levels by numerical diagonalization are plotted as green dots. The Dirac point lies at $6.4$eV. Parameters for (b): $m$: 0.05$\hbar^2$/eV$\cdot$\AA$^2$, $\alpha$: 0.05eV$\cdot$\AA, $Z_\parallel$: 0.04eV. (c) A sketch of cyclotron orbits of Rashba Hamiltonian with in-plane magnetic field. (d) For various configurations ($\alpha$, $Z_\parallel$) of $H_{RZ}$, we plot in left panel $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that is closest to $\epsilon_0$ in Eq. (\ref{whereisdiracpoint}), where $\epsilon_\text{rule}$ is determined by Eq. (\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian $H_{RZ}(\bK)$. Corresponding $l^2 \delta S^2/S$ are plotted in right panel. We only plotted in region where $0.4<\epsilon_0<1.0$(eV).\cite{RZfignote} Parameters for (d): $m$: 0.01$\hbar^2$/eV$\cdot$\AA$^2$, $l=100$\AA. \label{fig:RZ}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1.0\columnwidth]{blochsphere.png}
\caption{Solid-angle representation of  the single-band Berry phase $\phi_{\pm}^B$ for inner (subscript $-$, upper panel) and outer ($+$, lower panel) orbit, at various energies close to the Dirac point $\epsilon_0$ [cf.\ Eq. (\ref{whereisdiracpoint})]. The decomposition of the effective Hamiltonian [cf.\ Eq. (\ref{calHRZ})] into sums of Pauli matrices ($\calh{=}\sum_jd_j\sigma_j$) defines a three-vector $\bd{=}({-}\alpha k_y$,$Z_\parallel{+}\alpha k_x,{-}Z_\perp$).
 $\phi_{\pm}^B$  equals half the solid angle subtended by   ${\pm} \bd(\bk)$ \textbf{[I wasn't  careful about minus signs here]} as $\bk$ is varied along the outer/inner orbit.[Berry]   These angles are indicated in the figure by blue outlines.\label{fig:blochsphere}}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=1.0\columnwidth]{RD.png}
% alpha=0.05
% beta=0.02
% m=0.01
\caption{Rashba-Dresselhaus model. (a) Typical cyclotron orbits. (b) Comparison of Landau levels calculated by Eq. (\ref{eq:rule}) (black lines) and numerical diagonalization of the Peierls-Onsager Hamiltonian  $H_{RD}(\bK)$ (red dots). Parameters for (b): $\alpha=7.5$($10^{5}$cm$\cdot \hbar$/s), $m=0.076m_e$, $\beta=3~(6)$($10^{5}$cm$\cdot \hbar$/s) for left (right) panels. (c) For various spin-orbit parameters $(\alpha,\beta)$ of the Rashba-Dresselhaus model and various field strength (satisfying $l^2S(E)\gg 1$), we plot  $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that lies closest to energy $E=0.4eV$, where $\epsilon_\text{rule}$ is determined by Eq. (\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian  $H_{RD}(\bK)$. We also plot in (d) $l^2\delta S^2/S$, which has a strong positive relation with error in (c). Parameters for (c-d): $m=0.076m_e$. Units: $\alpha$($1.5\times 10^{5}$cm$\cdot \hbar$/s), $\beta$($1.5\times 10^{5}$cm$\cdot \hbar$/s), $Z$($10^{-3}$eV), $l^2 S$($10^2$).\label{fig:RD}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1.0\columnwidth]{RZ.png}
\caption{(a) Trefoille-shaped cyclotron orbit for the Rashba-Zeeman model at the energy of the Dirac point. The orbit is drawn over the  spin-splitting field ($d_x,d_y$) of the Hamiltonian $H_{RZ}{=}d_0(\bk)I{+}d_x(\bk)\sigma_x{+}d_y(\bk)\sigma_y$, with $d_j$ obtainable from \q{eq:RZ-Hamiltonian}. The wavefunction along the inner (resp.\ outer) component of the trefoille orbit has its pseudospin aligned parallel (resp.\ anti-parallel) to the spin-orbit field. (b) Black dashed lines illustrate a zeroth-order approximation of the Landau levels (assuming Klein tunneling); the leading-order correction is indicated by red lines. Exact Landau levels by numerical diagonalization are plotted as green dots. The Dirac point lies at $6.4$eV. Parameters for (b): $m$: 0.05$\hbar^2$/eV$\cdot$\AA$^2$, $\alpha$: 0.05eV$\cdot$\AA, $Z_\parallel$: 0.04eV. (c) A sketch of cyclotron orbits of Rashba Hamiltonian with in-plane magnetic field. (d) For various configurations ($\alpha$, $Z_\parallel$) of $H_{RZ}$, we plot in left panel $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that is closest to $\epsilon_0$ in Eq. (\ref{whereisdiracpoint}), where $\epsilon_\text{rule}$ is determined by Eq. (\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian $H_{RZ}(\bK)$. Corresponding $l^2 \delta S^2/S$ are plotted in right panel. We only plotted in region where $0.4<\epsilon_0<1.0$(eV).\cite{RZfignote} Parameters for (d): $m=0.076m_e$, $l=100$\AA. \label{fig:RZ}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1.0\columnwidth]{blochsphere.png}
\caption{Solid-angle representation of  the single-band Berry phase $\phi_{\pm}^B$ for inner (subscript $-$, upper panel) and outer ($+$, lower panel) orbit, at various energies close to the Dirac point $\epsilon_0$ [cf.\ Eq. (\ref{whereisdiracpoint})]. The decomposition of the effective Hamiltonian [cf.\ Eq. (\ref{calHRZ})] into sums of Pauli matrices ($\calh{=}\sum_jd_j\sigma_j$) defines a three-vector $\bd{=}({-}\alpha k_y$,$Z_\parallel{+}\alpha k_x,{-}Z_\perp$).
 $\phi_{\pm}^B$  equals half the solid angle subtended by   ${\pm} \bd(\bk)$ as $\bk$ is varied along the outer/inner orbit.[Berry]   These angles are indicated in the figure by blue outlines.\label{fig:blochsphere}}
\end{figure}
